Template for indicator documentation

### 2023-09-12 functional_plant_indicators_natopen.Rmd

# Functional plant indicators, naturally open ecosystems below the tree line (Grime's CSR values, Light, Nitrogen, Soil disturbance) {#Functional-plant-indicators-seminat}

>>>>

# Functional plant indicators, naturally open ecosystems below the tree line (Grime's CSR values, Light, Nitrogen, Soil disturbance) {#Functional-plant-indicators-open}

### 2023-09-12 functional_plant_indicators_wetland.Rmd

# make long version of the scaled value part
res.wetland <-
res.wetland %>%
pivot_longer(
cols = c("Light1","Light2","Moist1","Moist2","pH1","pH2","Nitrogen1","Nitrogen2"),
names_to = "fp_ind",
values_to = "scaled_value",
values_drop_na = TRUE
)

>>>>

# make long version of the scaled value part
res.wetland <-
res.wetland %>%
pivot_longer(
cols = c("Light1","Light2","Moist1","Moist2","pH1","pH2","Nitrogen1","Nitrogen2"),
names_to = "fp_ind",
values_to = "scaled_value",
values_drop_na = FALSE
)

### 2023-09-12 slitasje.Rmd

# (PART\*) INDICATORS{-}

# Slitasje og kjørespor

@@

```{r setup, include=FALSE}
library(knitr)
library(sf)
library(tmap)
library(ggpubr)
library(DT)
library(units)
library(eaTools)
library(stringr, lib.loc = "/usr/lib/R/site-library")
 library(tidyverse, lib.loc = "/usr/local/lib/R/site-library")
#library(tidyverse)
library(tibble)
knitr::opts_chunk$set(echo = TRUE)

>>>>

# Slitasje og kjørespor {#slitasje}

@@

```{r setup, include=FALSE}
library(knitr)
library(sf)
library(tmap)
library(ggpubr)
library(DT)
library(units)
library(eaTools)
library(tidyverse)
library(tibble)
knitr::opts_chunk$set(echo = TRUE)
